\LARGE \bf Multi-Armed Bandit Models for Sample-Based Grasp Planning in the Presence of Uncertainty [v-14 09-30-2014]

### 2014-10-02 paper.tex
got rid of todos

\todo{ref figure}

@@

\subsection{Line of action}
Similar to the work of \cite{christopoulos2007handling}, we assume that each gripper finger approaches along a \textit{line of action}, a 1D curve $\gamma(t)$ with endpoints $a$ and $b$ as seen in Fig. \ref{fig:line_of_action}.
A gripper finger starts at point $a$ and moves towards $b$, we assume $a$ is far enough away to be collision free of the object.
Each gripper contact is defined by a line of action, so we assume the following tuple is provided $\Gamma = ( \gamma_1(\cdot),...,\gamma_m(\cdot) )$, which designates a proposed \textit{grasp plan}.
\todo{move the next two lines}
While we currently assume the gripper moves free of noise, this approach would be applicable to high precision robots such as industrial based on. 
Future work will look at how to efficiently sample when the approach trajectory has noise.

@@

In solving Eq. \ref{eq:problem_def}, we want to pick the grasp plan with the highest $E(Q(\Gamma))$ determined via Monte-Carlo Integration.
Due to the non-linear nature of our grasp metric, we currently do not have a way to represent the distribution on grasp quality of $p(Q(\Gamma))$ in closed form.
Thus, we are restricted in the type of bandit policies available to us, since most sophisticated polices require distributional information. \todo{double check with Dylan}

@@

The $L^1$ version of the metric works by taking as input the contact points $\textbf{c}_1,...,\textbf{c}_m$, surface normals $\textbf{n}_1,...,\textbf{n}_m$, center of mass $z$ and friction coefficient $\mu$. Then constructing a convex hull around the wrenches made up of those parameters and finding the radius of the largest unit ball centered at the origin in wrench space. A wrench is defined as concatenation of a force and torque vector.  If the convex hull doesn't enclose the origin, the grasp is not in force-closure. Thus a grasp can be parameterized by the following tuple $g = \lbrace \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, \textbf{z} \rbrace$, our method is applicable to all grasp metrics that represent a grasp as the tuple $g$, such as \cite{christopoulos2007handling}, \cite{li1988task}.

@@

To reduce complexity we propose sampling not from the shape distributions, but instead from the distributions on the grasps parameters themselves. We recall that a grasp according to our metric is defined as the tuple $g = \lbrace \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, z \rbrace$. We are thus interested in calculating $p(g|\Gamma,\mu(x),\Sigma(x))$. The distribution on a grasp is defined then as:

>>>>

@@

\subsection{Line of action}
Similar to the work of \cite{christopoulos2007handling}, we assume that each gripper finger approaches along a \textit{line of action}, a 1D curve $\gamma(t)$ with endpoints $a$ and $b$ as seen in Fig. \ref{fig:line_of_action}.
A gripper finger starts at point $a$ and moves towards $b$, we assume $a$ is far enough away to be collision free of the object.
Each gripper contact is defined by a line of action, so we assume the following tuple is provided $\Gamma = ( \gamma_1(\cdot),...,\gamma_m(\cdot) )$, which designates a proposed \textit{grasp plan}.
While we currently assume the gripper moves free of noise, this approach would be applicable to high precision robots such as industrial based on. 
Future work will look at how to efficiently sample when the approach trajectory has noise.

@@

In solving Eq. \ref{eq:problem_def}, we want to pick the grasp plan with the highest $E(Q(\Gamma))$ determined via Monte-Carlo Integration.
Due to the non-linear nature of our grasp metric, we currently do not have a way to represent the distribution on grasp quality of $p(Q(\Gamma))$ in closed form.

@@

The $L^1$ version of the metric works by taking as input the contact points $\textbf{c}_1,...,\textbf{c}_m$, surface normals $\textbf{n}_1,...,\textbf{n}_m$, center of mass $z$ and friction coefficient $\mu$. Then constructing a convex hull around the wrenches made up of those parameters and finding the radius of the largest unit ball centered at the origin in wrench space. A wrench is defined as concatenation of a force and torque vector.  If the convex hull doesn't enclose the origin, the grasp is not in force-closure. Thus a grasp can be parameterized by the following tuple $g = ( \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, \textbf{z} )$, our method is applicable to all grasp metrics that represent a grasp as the tuple $g$, such as \cite{christopoulos2007handling}, \cite{li1988task}.

@@

To reduce complexity we propose sampling not from the shape distributions, but instead from the distributions on the grasps parameters themselves. We recall that a grasp according to our metric is defined as the tuple $g = ( \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, z )$. We are thus interested in calculating $p(g|\Gamma,\mu(x),\Sigma(x))$. The distribution on a grasp is defined then as:
